Methods for Large Scale Learning to Rank

### 2014-09-25 report/Chapters/Introduction.tex
bigskips om RQs heen

\begin{description}
\item[RQ1] What are the best performing Learning to Rank algorithms in terms of ranking accuracy on relevant benchmark data sets?
\end{description}

There are several existing metrics that can be used to express the accuracy of a ranking, which we will explore in section \ref{sec:how_to_evaluate_a_ranking}.

\begin{description}
\item[RQ2] What is the speed-up of those Learning to Rank algorithms when executed using the MapReduce framework?
\end{description}
With multiple existing definitions of speed-up, we will use the speed-up definition known as \emph{relative speed-up} \cite{Sun1991}, which is formulated as follows:\\

>>>>

\begin{description}
\item[RQ1] What are the best performing Learning to Rank algorithms in terms of ranking accuracy on relevant benchmark data sets?
\end{description}
\bigskip
Ranking accuracy is an ambiguous concept, as there exists several metrics that can be used to express the accuracy of a ranking. We will explore several metrics for ranking accuracy in section \ref{sec:how_to_evaluate_a_ranking}.\\

\begin{description}
\item[RQ2] What is the speed-up of those Learning to Rank algorithms when executed using the MapReduce framework?
\end{description}
\bigskip
With multiple existing definitions of speed-up, we will use the speed-up definition known as \emph{relative speed-up} \cite{Sun1991}, which is formulated as follows:\\
